\documentclass[a4paper,10pt]{article}

%-----------------------------------------------------------
% PACKAGES
%-----------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}

% Page margins
\geometry{left=0.5in, top=0.4in, right=0.5in, bottom=0.4in}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-----------------------------------------------------------
% CUSTOM COMMANDS (Used by resumeController.js)
%-----------------------------------------------------------
\newcommand{\resheading}[1]{
  \vspace{8pt}
  {\color{black} \textbf{\large #1}}
  \vspace{-5pt}
  \hrulefill
  \vspace{3pt}
}

\newcommand{\ressubheading}[4]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resitem}[1]{
  \item \small{
    {#1 \vspace{-2pt}}
  }
}

%-----------------------------------------------------------
% RESUME START
%-----------------------------------------------------------
\begin{document}

%--- HEADER ---
\begin{center}
    \textbf{\Huge Srijan Basu} \\ \vspace{3pt}
    \small +91 9088801139 $|$ \href{mailto:2003srijanbasu@gmail.com}{{{EMAIL}}} $|$ 
    \href{https://}{LinkedIn} $|$ 
    \href{https://}{GitHub} 
\end{center}

%--- SUMMARY ---
\resheading{SUMMARY}
\small • Full Stack Developer Intern at Callsure.ai building a voice-first healthcare platform and multi-tenant hospital management workflows.
• Strong backend focus: FastAPI layered architecture, REST APIs, database schema design, and OTP authentication using DynamoDB TTL.
• Frontend experience building React dashboards for admins and staff; comfortable with Docker, Git/GitHub, Swagger UI, and Postman.


%--- EDUCATION ---
\resheading{EDUCATION}
\begin{itemize}[leftmargin=*,nosep]
\item[] \ressubheading{Brainware University}{Sep 2025 – 2027 (Expected)}{Master of Computer Applications (MCA)}{CGPA: 8.38}
\item[] \ressubheading{Techno India University, Salt Lake}{Sep 2022 – May 2025}{Bachelor of Computer Applications (BCA Honors)}{CGPA: 7.47}
\end{itemize}

%--- EXPERIENCE ---
\resheading{EXPERIENCE}
\begin{itemize}[leftmargin=*,nosep]
\item[] \ressubheading{Callsure.ai}{Sep 2025 – Present}{Full Stack Developer Intern}{Remote}
\begin{itemize}[leftmargin=12pt,nosep,topsep=2pt]
  \resitem{Engineered a voice-first healthcare platform, enhancing AI-assisted appointment booking via REST APIs.}
  \resitem{Designed a multi-tenant hospital management system for multiple clinics and concurrent users.}
  \resitem{Implemented scalable backend services using FastAPI with layered architecture.}
  \resitem{Architected relational schemas for hospitals, users, and appointment workflows.}
  \resitem{Integrated OTP authentication using DynamoDB with TTL-based auto-expiry.}
  \resitem{Developed React dashboards for admins and staff to manage schedules and appointments.}
  \resitem{Documented and tested over 15 REST APIs using Swagger UI and Postman.}
\end{itemize}
\item[] \ressubheading{LTIMindtree}{Jun 2025 – Aug 2025}{Cloud Infrastructure Service Engineer}{On-Site}
\begin{itemize}[leftmargin=12pt,nosep,topsep=2pt]
  \resitem{Utilized enterprise IT tools including WSUS, MECM, OKTA, Active Directory, and Microsoft 365.}
  \resitem{Supported cloud infrastructure operations and IT service management processes.}
\end{itemize}
\end{itemize}

%--- PROJECTS ---
\resheading{PROJECTS}
\begin{itemize}[leftmargin=*,nosep]
\item[] \ressubheading{Resumware – AI-Powered ATS Resume Builder}{Feb 2025 – May 2025}{Technologies: }{}
\begin{itemize}[leftmargin=12pt,nosep,topsep=2pt]
  \resitem{Developed an AI-powered resume builder generating ATS-friendly resumes using LaTeX templates.}
  \resitem{Integrated Gemini 1.5 Flash for automated resume content creation and formatting.}
  \resitem{Built a responsive frontend using React and Tailwind CSS.}
  \resitem{Designed REST APIs with Node.js, Express.js, and TypeScript.}
  \resitem{Managed resume data with MongoDB for scalable content handling.}
  \resitem{Deployed the application on Netlify and Vercel using Git-based workflows.}
\end{itemize}
\item[] \ressubheading{Daily Finance Collection App}{May 2024 – Jul 2024}{Technologies: }{}
\begin{itemize}[leftmargin=12pt,nosep,topsep=2pt]
  \resitem{Created a finance tracking app for daily income and expense management.}
  \resitem{Implemented backend with Django and frontend using HTML, CSS, and JavaScript.}
  \resitem{Adopted by small businesses for tracking daily financial transactions.}
\end{itemize}
\end{itemize}

%--- SKILLS ---
\resheading{SKILLS}
\begin{itemize}[leftmargin=12pt,nosep,topsep=2pt]
  \item[] \small \textbf{Languages:} Python, JavaScript, TypeScript, C/C++, Java
  \item[] \small \textbf{Backend \& APIs:} FastAPI, Node.js, Express.js, RESTful API design, layered architecture
  \item[] \small \textbf{Frontend:} React, Next.js, Tailwind CSS
  \item[] \small \textbf{Databases \& Auth:} MongoDB, DynamoDB (TTL-based OTP authentication), relational schema design
  \item[] \small \textbf{Architecture:} Multi-tenant systems, scalable API development
  \item[] \small \textbf{AI \& Docs:} Gemini 1.5 Flash API, LaTeX-based document rendering
  \item[] \small \textbf{Tools:} Git/GitHub, Docker, Swagger UI (OpenAPI), Postman
  \item[] \small \textbf{Deployment:} Vercel, Netlify, AWS (basic)
\end{itemize}

%--- ADDITIONAL SECTIONS ---




\resheading{CERTIFICATIONS}
\begin{itemize}[leftmargin=12pt,nosep,topsep=2pt]
  \resitem{Oracle Cloud Infrastructure 2025 Certified AI Foundations Associate — Oracle (Oct 06, 2025; valid until Oct 06, 2027) | Credential ID: 102823593OCI25AICFA | Source}
  \resitem{AI-ML Virtual Internship (10 weeks) — AICTE–EduSkills (Supported by Google for Developers), Jul–Sep 2024 | Certificate ID: 38bc9b798a89cec23571566924b061c7 | Source}
  \resitem{HTML Test (Times of India) — Campus Technology (Apr 30, 2025) | Source}
\end{itemize}

\end{document}